\cvsection{Experience}
\begin{cventries}
\cventry
    {Software Developer Intern}
    {theScore Inc.}
    {Toronto, Canada}
    {Aug. 2016 -  Dec. 2016}
    {
      \begin{cvitems}
        \item {Developed a \textit{\href{http://www.m.me/thescore}{Facebook chatbot}} that delivers live score updates and breaking news for sports teams.}
       \item {Developed key features which increased \textbf{daily active users from 500 to 65000+} and increased percentage of users that follow a sports team by 10+\%.}
        \item {Built infrastructure to easily add new sports to the chatbot and used this infrastructure to add cricket. \textit{\textbf{Ruby on Rails}}}
        \item {Presented the chatbot architecture to the entire engineering team and offered ideas on how to improve it.}
      \end{cvitems}
    }
  \cventry
    {Software Developer Intern}
    {PharmAchieve}
    {Toronto, Canada}
    {Jan. 2016 -  Apr. 2016}
    {
      \begin{cvitems}
        \item {\textbf{Sole developer at the company} which provides test prep for pharmacy students.}
        \item {Developed interactive data visualizations of user data. \textit{\textbf{D3.js}}}
        \item {Designed and developed a quiz generator which enabled students to create custom quizzes on the topics of their liking. }
        \item {Created PharmAchieve's first REST API which \textbf{automated complex processes} through simple API calls such as recommended reading for students based on past performance. \textit{\textbf{Node.js, Express}} }
      \end{cvitems}
    }
  \cventry
    {Software Developer Intern}
    {Thinkingbox}
    {Toronto, Canada}
    {May 2015 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Created the \textbf{official site for Mission Impossible 5} within a month. The site won a \textit{\href{https://www.w3award.com/winners/list/view/?event=31&award=1&_p=8}{'Gold Awwward'}} for best movie site. \textit{\textbf{ReactJS, Flux}}}
        \item {Expanded existing backend for project 'UBC Your Evolution' to allow users to collaborate, display projects and connect with others.}
       \item {Non-development: Generated over 50 leads alongside the Director for New Business to expand company to new verticals.}
      \end{cvitems}
    }
  \cventry
    {Head Volunteer}
    {Sanshil Foundation for Welfare}
    {Gurgaon, India}
    {Dec. 2011 - July 2013}
    {
      \begin{cvitems}
        \item {Worked for the NGO which teaches and finances underprivileged children so that they can join mainstream schools.}
        %\item {Managed all volunteers, planned all activities and daily tasks including teaching content.}
        %\item{Raised more than 60,000 Rs. (1000 USD) for the organization in addition to over 500 textbooks.}
        \item {Developed an \textbf{Android application to teach language skills} through video examples and quizzes. Prototype sent to Macmillan Publishers.}
      \end{cvitems} 
    }
\end{cventries}