\cvsection{Projects}
\begin{cvskills}
  \cvskill
    {Yoffee}
    {
	Ping your coffee machine from your smartwatch or phone to start brewing coffee for you.  \textit{\textbf{Raspberry Pi, Arduino}}
    }
\cvskill
{}
{
	\textit{\textbf{PHP}}
}
\cvskill
    {Compiler}
    { 
	Created compiler for a subset of C. Supports arithmetic, conditionals, loops,
}
\cvskill
{}
{
 functions and overloading. Implemented variable folding to reduce compiled file size by factor of 5. \textit{\textbf{C++}}
    }
  \cvskill
    {Facesnoop}
    {
        Browser extension which blocks ‘seen’ notification in the Facebook web chat. \textit{\textbf{JavaScript}}  
    }
\cvskill
    {Showersong}
    {
	Android app that suggests songs to sing in the shower through text-to-speech. Used Lastfm API to get your
}
\cvskill
{}
{
 most played songs. \textit{\textbf{Android, Java}}
    }
 \cvskill
    {Readdit}
    {
       Created handsfree navigation for the first edition of Pebble watches using in-built accelerometer and Pebble SDK
}
\cvskill
{}
{
 in C. Developed a Reddit app for Pebble to demonstrate the application in JavaScript. \textit{\textbf{Pebble SDK, C, JavaScript}}
    }
  \cvskill
    {Drivers2Go}
    { 
        Android app which allows non-English speaking taxi drivers to communicate with English speaking customers
}
\cvskill
{}
{
  through a simple interface. \textbf{Three major taxi companies agreed to use the app} in their training programs for over
    }
\cvskill
{}
{
1000 drivers.  \textit{\textbf{Android, Java}}      
}
\end{cvskills}
